### 2021-02-18 architecture.tex
Architecture: Explain graphification

\subsection{Precedence generator}

@@

\subsection{Graph representation of problems}

\todo{MS: HIN bych povazoval za pro CADE-people neznamuy pojem.
Bude treba uvest aspon jednou vetou. Mozna neco citovat?}

Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
\todo{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
ale my nevime, jak takovy zvolit. }

\begin{figure}[ht]
\caption{CNF network schema}
\label{fig:CnfSchema}
\centering
\tikzstyle{token} = [rectangle, draw]

The network of a problem is a directed graph $G = (V, E)$.
The function $\tau: V \rightarrow A$ maps the nodes to their types:

$$
A = \{\ntype{problem}, \ntype{predicate}, \ntype{function}, \ntype{clause}, \ntype{atom}, \ntype{equality}, \ntype{term}, \ntype{variable}, \ntype{argument}\}
$$

The function $\phi: E \rightarrow E$ maps the edges to their types.

\todo[inline]{Abstract from the edge types. Focus on the main idea. Technical details may be in technical report or appendix.}

Various levels of term sharing are possible. [continue]

>>>>

\subsection{From \gls{cnf} to graphs}

As the first step of the recommender processing pipeline,
the input problem is converted from a \gls{cnf} representation
to a \emph{heterogeneous directed graph}.\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
\todo{FB: Consider removing the footnote because it is basically useless.}
Each of the nodes is labeled with a node type,
and each edge is labeled with an edge type,
informing the heterogeneous nature of the graph.
The nodes of the graph correspond to various elements that constitute the \gls{cnf} formula,
such as clauses, atoms and predicate symbols.
Each such category of elements corresponds to one node type.
The edges represent the (oriented) relations between the elements,
for example the relation between a clause and one of its atoms,
or the relation between an atom and its predicate symbol.
\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.

\begin{figure}[h]
\caption{CNF network schema}
\label{fig:CnfSchema}
\centering
\tikzstyle{token} = [rectangle, draw]

The graph representation has the following properties:
\begin{itemize}
\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
represented by a different edge type (unless $r = \inv{r}$ is an identity).
% Note: The relation is considered an identity if it is a subset of the complete identity relation.
\item Lossless: The original problem can be reconstructed from the graph representation completely
(up to equivalent modifications).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Term-sharing is employed: Redundant atoms and terms share a node representation \cite{}.
Note that since each variable is bound by a clause,
ground terms may be shared across clauses,
but non-ground terms may only be shared within a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo[inline]{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
ale my nevime, jak takovy zvolit. }

@@
